Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2021-12-22 manuscript.tex
TL minor edits

In this paper, we consider the motion of a dumbbell model of spacecraft around an asteroid.
The dumbbell model captures the important interactions of the coupling between orbital and attitude dynamics.
The dumbbell is defined by two spherical masses of radius \( r_1, r_2 \in \R \) with masses \( m_1, m_2 \in  \R\).
The masses are separated by a massless rod of length \( l \) and attached to the centers of each mass.
\Cref{fig:dumbbell_sc} shows the model and associated parameters.
\begin{figure}[htbp]
    \centering
    \input{dumbbell.tikz}
    \caption{Dumbbell Model of Rigid Spacecraft\label{fig:dumbbell_sc}}
\end{figure}
The dumbbell model is in some sense the simplest approximation of an extended rigid body.
This model captures the important dynamics of an extended rigid body with a minmum of additional complexity and is prevelant the literature~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
In addition, the developments of the dumbbell model can be trivially extended to include a larger number of discrete masses to better approximate a more complicated spacecraft model.

@@

Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
\begin{align}
    \dot{\vc{x}} &= \vc{v}, \label{eq:x_dot}\\
    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
    \dot{R} &= R S(\vc{\Omega}) , \label{eq:R_dot}\\
    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m. \label{eq:omega_dot}
\end{align}
The vectors \( \vc{z}_1 \) and \( \vc{z}_2\in\Re^3\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
\begin{align}
    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2},
\end{align}
where \( \rho_i \in\Re^3 \) defines the position of each mass in the spacecraft fixed body frame.
The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
The standard moment of inertia of the dumbbell model is 
\begin{align}\label{eq:dumbbell_moment_of_inertia}
    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I - \vc{\zeta}_i \vc{\zeta}_i^T} , 
\end{align}
where \( \vc{\zeta}_i \) is the position of \( m_i \) in the spacecraft fixed frame and the moment of inertia of each sphere is
\begin{align}\label{eq:sphere_moment_of_inertia}
    J_i = \begin{bmatrix} 
        \frac{2}{5} m_i r_i^2 & 0 & 0 \\
        0 & \frac{2}{5} m_i r_i^2 & 0 \\
        0 & 0 & \frac{2}{5} m_i r_i^2 
    \end{bmatrix}.
\end{align}
\Cref{eq:dumbbell_moment_of_inertia} is consistent with the well-known parallel-axis theorem~\cite{greenwood1988}.
We utilize a nonstandard moment of inertia in the equations of motion, \( J_d \in \R^{3 \times 3 } \), which is related to the standard moment of inertia by
\begin{subequations}\label{eq:moi_transformation}
    \begin{align}
        J &= \tr{J_d} I - J_d, \label{eq:moi_ns2s}\\
        J_d &= \frac{1}{2} \tr{J} I - J.\label{eq:moi_s2ns}
    \end{align}
\end{subequations}     
The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
\begin{align}
    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}
In the above equations, the gravitational potential is denoted by $U\in\Re$, which is computed by a polyhedron model as described in the subsequent section.

@@

One of the first tasks for any spacecraft mission to a small body is to generate an estimate of the shape.
We assume that upon arrival at a target body, the spacecraft contains an initial estimate for the shape of the small body.
This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
Additionally, we assume that the shape estimate is closed and a triangular faceted surface mesh, emulating those used in practice to represent asteroids.
Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
In this section, we present a stochastic formulation to update the initial estimate of the shape incrementally based on range measurements from spacecraft in real time.

@@

We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
Recent missions such as OSIRIS-REx have featured a scanning LIDAR system which allows for much higher measurement rates compared to previous missions~\cite{lauretta2017,daly2017}.
In these mission, ranging measurements are combined with imagery to derive a shape model using a ground based method~\cite{gaskell2008}.
In constrast to previous missions, the scanning LIDAR system on OSIRIS-REx enables for high surface sample rates in spite of the low ground-track velocities~\cite{daly2017}.
This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
Given the time total time of flight, the distance can be accurately computed using \( d = \frac{\Delta TOF }{2} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
The output of this sensor is a vector, \( \vc{d}_i\in\Re^3 \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
\begin{align*}
    \vc{p}_i = R_A^T (x+R \vc{d}_i), 
\end{align*}
which is the vector from the origin of the asteroid fixed frame to the surface point of the measurement.

Given many measurements, \( \vc{p}_i \in \R^3 \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
\Cref{fig:lidar_example} shows asteroid 4769 Castalia and a representation of several LIDAR measurements. 
The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
These measurements provide a collection of points which lie on the surface of the asteroid, and by combining many points, a so called \textit{point cloud}, allows us to reconstruct the shape.
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{castalia_raycasting_plot.jpg}
    \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
\end{figure}

@@

In order to reduce the computational demands, which are typical in point cloud applications, we do not update the complete shape model for each measurement.
Instead we define an area of interest, \( \Delta S\in\Re \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
We relate \( \Delta S \) to an equivalent angular constraint using
\begin{align}\label{eq:region_of_interest}
    \Delta \sigma_{max} = \sqrt \frac{\Delta S}{r_b^2}
\end{align}
% shankar: brillouin is correct. https://arc.aiaa.org/doi/10.2514/6.2014-4302
where \( r_b \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update defined as follows.

Each measurement is defined by the index \( j \) while the associated vertex satisfying \cref{eq:region_of_interest} is defined by \( i \). 
As a result, the measurement \( p_{j, i} \) defines the distribution of measurement \( j \) with respect to vertex \( i \). 
The radial distance of each measurement, \( p_{j,i} = \norm{\vc{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
\begin{align*}
    p_{j,i} \sim \mathcal{N}(r_{j,i}, w_{j,i}^2)
\end{align*}
where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i}\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).

@@

From Bayes' theorem, the a posterior probability of the vertex radius is given by
\begin{align}
    p(v_i | p_{j, i}) = \frac{p(p_{j, i} | v_i) p(v_i)}{p( p_{j, i})} \propto p(p_{j,i} | v_i) p(v_i).
\end{align}
From the properties of Gaussian distributions, the posterior probability given a measurement is also distributed according to a Gaussian distribution~\cite{bishop2006} and given by
\begin{align}\label{eq:posterior_probability}
    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2  w_{j, i}^2}{w_i^2 +  w_{j, i}^2}} .
\end{align}
From~\cref{eq:posterior_probability}, the a posterior mean conditioned on the measurement is the average of the prior knowledge and the measurement weighted by the reciprocal of the variance. 
As such, it will be closer to the value with a smaller variance. 
For example, measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.

@@

The results in this section utilize a kinematics only model of the spacecraft instead of the full dynamical simulation. 
We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction, and the spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
The spacecraft remains at a fixed orbital radius defined as twice the maximum semi-major axis of the asteroid.
The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
LIDAR measurements are generated until the total uncertainty of the model
\begin{align*}
    \sum_i w_i,
\end{align*}
is sufficiently small.
This uncertainty metric is the summation of the uncertainty of each vertex of the shape estimate.
As a result, a small total uncertainty is used to indicate that additional measurements would not substantially modify the shape.
In addition, we compute the volume of the estimated shape and compare against the volume of the truth shape model~\cite{neese2004}.

@@

\paragraph{Asteroid \num{1620} Geographos Reconstruction} 
\num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
\Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
Comparing~\cref{fig:geographos_partial_100,fig:geographos_truth} shows that the final shape closely matches the true radar model.
In~\cref{fig:geographos_metrics} we display the vertex uncertainty and mesh volume as a function of time.
The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.

@@

\paragraph{Asteroid \num{6489} Golevka Reconstruction} 
Next, \num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
Discovered in \num{1995}, Golevka is a potentially hazardous asteroid which passes sufficiently close to the Earth to present a hazard.
\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_1321.jpg}}\\%

@@

We define a cost associated with each vertex \( \vc{v}_i \) of the shape estimate as
\begin{align}\label{eq:explore_cost}
    J_i (x, R, R_A) = \alpha_w J_{w_i} + \alpha_d J_{d_i}(x_r) + \alpha_c J_{c_i}(x_r)
\end{align}
where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R^1 \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
The cost function is defined as a function of the current inertial position, \( x \in \R^3 \), and the attitude, \( R \in \R^{3\times3}\) of the spacecraft.
Furthermore, knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( x_r = R_A^T x\).

@@

Finally, a control component is included in the cost function which penalizes vertices that are difficult to reach.
Consider, the current position of the spacecraft in the small body fixed frame as \( \rpos\) and a desired vertex \( \vc{v}_i \) of the shape estimate.
We can define a normal vector to the plane spanned by \( \rpos, \vc{v}_i \) as
\begin{align}\label{eq:normal_to_plane}
    \vc{n}_i = \frac{\rpos \times \vc{v}_i}{\norm{\rpos} \norm{\vc{v}_i}}.
\end{align}
Then a desired trajectory \( x_d(\theta) \) as
\begin{align}\label{eq:spherical_waypoint}
    x_d(\theta) = r_d \exp{\parenth{\theta \hat{\vc{n}_i}} } \frac{\rpos}{\norm{\rpos}},
\end{align}
where \( \theta : \bracket{0, \frac{\rpos \cdot \vc{v}_i}{\norm{\rpos}\norm{\vc{v}_i}}} \to \R^1\) parameterizes the desired trajectory.
\Cref{eq:spherical_waypoint} simply describes a portion of a great circle trajectory between the current state, \( \rpos \), and the desired vertex \( \vc{v}_i \)~\cite{chen2016}, with a desired radius $r_d$.
The radius of the spacecraft, \( r_d \in \R \), can be chosen based on sensor characteristics of safety concerns.
For example, \( r_d \) can be chosen as the distance of the Biroullin sphere with an additional safety margin to mitigate any surface collision~\cite{scheeres2012a}.

@@

The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations. 
In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
This approach allows for a spacecraft to autonomously select and land on small body.

The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
At the center of each face, \( f_i = [ f_x,\,  f_y,\,  f_z ] \), we compute a modified surface acceleration as
\begin{align}\label{eq:surface_force}
    U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
\end{align}
where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
Then the surface slope can be computed from
\begin{align}\label{eq:surface_slope}
    \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
\end{align}
where \( \phi \in \R^1 \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.

>>>>

In this paper, we consider the motion of a dumbbell model of spacecraft around an asteroid.
The dumbbell is defined by two spherical masses of radius \( r_1, r_2 \in \R \) with masses \( m_1, m_2 \in  \R\).
The masses are separated by a massless rod of length \( l \) and attached to the centers of each mass.
\Cref{fig:dumbbell_sc} shows the model and associated parameters.
\begin{figure}[htbp]
    \centering
    \input{dumbbell.tikz}
    \caption{Dumbbell Model of Rigid Spacecraft\label{fig:dumbbell_sc}}
\end{figure}
The dumbbell model is in some sense the simplest approximation of an extended rigid body.
This model captures the important dynamics of an extended rigid body with a minmum of additional complexity and is prevelant the literature~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
In addition, the developments of the dumbbell model can be trivially extended to include a larger number of discrete masses to better approximate a more complicated spacecraft model.

@@

Using Hamilton's principle one can derive the inertial equations of motion of the dumbbell spacecraft~\cite{kulumani2017b} as
\begin{align}
    \dot{\vc{x}} &= \vc{v}, \label{eq:x_dot}\\
    \parenth{m_1 + m_2} \dot{\vc{v}} &= m_1 R_A \deriv{U}{\vc{z}_1} + m_2 R_A \deriv{U}{\vc{z}_2} + u_f,\label{eq:v_dot} \\
    \dot{R} &= R S(\vc{\Omega}) , \label{eq:R_dot}\\
    J \dot{\vc{\Omega}} + \vc{\Omega} \times J \vc{\Omega} &= \vc{M}_1 + \vc{M}_2 + u_m. \label{eq:omega_dot}
\end{align}
The vectors \( \vc{z}_1 \) and \( \vc{z}_2\in\Re^3\) define the position of the dumbbell masses in the asteroid fixed frame and are defined as
\begin{align}
    \vc{z}_1 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_1} , \\
    \vc{z}_2 &= R_A^T \parenth{\vc{x} + R \vc{\rho}_2},
\end{align}
where \( \rho_i \in\Re^3 \) defines the position of each mass in the spacecraft fixed body frame.
The control inputs to the spacecraft are defined by \( u_f, u_m \in \Re^3 \) which define the control force represented in the inertial frame and the control moment represented in the spacecraft frame, respectively.
The standard moment of inertia of the dumbbell model is 
\begin{align}\label{eq:dumbbell_moment_of_inertia}
    J_I = \sum_i^n J_i + m_i \parenth{\vc{\zeta}_i^T \vc{\zeta}_i I_{3\times 3} - \vc{\zeta}_i \vc{\zeta}_i^T} , 
\end{align}
where \( \vc{\zeta}_i \) is the position of \( m_i \) in the spacecraft fixed frame and the moment of inertia of each sphere is
\begin{align}\label{eq:sphere_moment_of_inertia}
    J_i = \begin{bmatrix} 
        \frac{2}{5} m_i r_i^2 & 0 & 0 \\
        0 & \frac{2}{5} m_i r_i^2 & 0 \\
        0 & 0 & \frac{2}{5} m_i r_i^2 
    \end{bmatrix}.
\end{align}
\Cref{eq:dumbbell_moment_of_inertia} is consistent with the well-known parallel-axis theorem~\cite{greenwood1988}.
We utilize a nonstandard moment of inertia in the equations of motion, \( J_d \in \R^{3 \times 3 } \), which is related to the standard moment of inertia by
\begin{subequations}\label{eq:moi_transformation}
    \begin{align}
        J &= \tr{J_d} I_{3\times 3} - J_d, \label{eq:moi_ns2s}\\
        J_d &= \frac{1}{2} \tr{J} I_{3\times 3} - J.\label{eq:moi_s2ns}
    \end{align}
\end{subequations}     
The gravitational moment on the dumbbell \( \vc{M}_i\) is defined as
\begin{align}
    \vc{M}_i = m_i \parenth{S(R_A^T \vc{\rho}_i) R^T \deriv{U}{\vb{z}_i}}.
\end{align}
In the above equations, the gravitational potential is denoted by $U\in\Re$, which is computed by a polyhedron model as described in the subsequent section.

@@

One of the first tasks for any spacecraft mission to a small body is to generate an estimate of the shape.
We assume that upon arrival at a target body, the spacecraft contains an initial estimate for the shape of the small body.
This shape can be a coarse estimate computed from ground measurements or it can be a triaxial ellipsoid based on the semimajor axes of the asteroid.
Additionally, we assume that the shape estimate is a triangular faceted, closed surface mesh, emulating those used in practice to represent asteroids.
Furthermore, the number of vertices in the estimate can be scaled according to the desired final accuracy or computational capabilities.
In this section, we present a stochastic formulation to update the initial estimate of the shape incrementally based on range measurements from spacecraft in real time.

@@

We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
Recent missions such as OSIRIS-REx have featured a scanning LIDAR system which allows for much higher measurement rates compared to previous missions~\cite{lauretta2017,daly2017}.
In these mission, ranging measurements are combined with imagery to derive a shape model using a ground based method~\cite{gaskell2008}.
In constrast to previous missions, the scanning LIDAR system on OSIRIS-REx enables for high surface sample rates in spite of the low ground-track velocities~\cite{daly2017}.
This type of sensor measures the round-trip time for a pulse of energy to leave the spacecraft, reflect off the surface, and return to a collector on board.
Given the time total time of flight ($\Delta TOF$) the distance can be accurately computed using \( d = \frac{c \Delta TOF }{2} \) where \( c = \SI{2.998e8}{\meter\per\second}\) is the constant speed of light.
Assuming accurate knowledge of the pointing direction of the spacecraft, in the form of the rotation matrix \( R \in \R^{3 \times 3 } \), we can compute a direction from the spacecraft to the measurement location on the surface.
The output of this sensor is a vector, \( \vc{d}_i\in\Re^3 \), defined in the spacecraft fixed frame which gives the direction to a measurement point on the surface. 
Using the state of the asteroid, we can transform this measurement to the asteroid fixed frame using the simple transformation
\begin{align*}
    \vc{p}_i = R_A^T (x+R \vc{d}_i), 
\end{align*}
which is the vector from the origin of the asteroid fixed frame to the surface point of the measurement.

Given many measurements, \( \vc{p}_i \in \R^3 \), of the asteroid surface we can efficiently update our initial shape estimate to that of the true surface.
\Cref{fig:lidar_example} shows asteroid 4769 Castalia and a representation of several LIDAR measurements. 
The spacecraft measures the range between itself and the asteroid surface to several points within the field of view of the sensor. 
These measurements provide a collection of points to form so called \textit{point cloud}, which allows us to reconstruct the shape.
\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{castalia_raycasting_plot.jpg}
    \caption{Simulated LIDAR measurements of asteroid Castalia~\label{fig:lidar_example}}
\end{figure}

@@

In order to reduce the computational demands, which are typical in point cloud applications, we do not update the complete shape model for each measurement.
Instead we define an area of interest, \( \Delta S\in\Re \), about each measurement which defines the surface area over which the measurement will affect the mesh estimate.
We relate \( \Delta S \) to an equivalent angular constraint using
\begin{align}\label{eq:region_of_interest}
    \Delta \sigma_{max} = \sqrt \frac{\Delta S}{r_b^2}
\end{align}
% shankar: brillouin is correct. https://arc.aiaa.org/doi/10.2514/6.2014-4302
where \( r_b \in \Re \) defines the Brillouin  sphere radius, or the radius of the circumscribing sphere of the asteroid.
Only vertices which satisfy \( \Delta \sigma_i \leq \Delta \sigma_{max} \) are considered in the Bayesian update defined as follows.

Each measurement is defined by the index \( j \) while the associated vertex satisfying \cref{eq:region_of_interest} is defined by \( i \). 
As a result, the measurement \( p_{j, i} \) defines the distribution of measurement \( j \) with respect to vertex \( i \). 
The radial distance of each measurement, \( p_{j,i} = \norm{\vc{p}_j}\), is also assumed to be distributed according to the Gaussian distribution
\begin{align*}
    p_{j,i} \sim \mathcal{N}(r_{j,i}, w_{j,i}^2)
\end{align*}
where \( r_{j,i} = \norm{\vc{p}_{j,i}} \) defines the radial distance of the surface vector measurement and \( w_{j, i} \in\Re\) defines the variance of the measurement with respect to vertex \( \vc{v}_i\).

@@

From Bayes' theorem, the a posteriori probability of the vertex radius is given by
\begin{align}
    p(v_i | p_{j, i}) = \frac{p(p_{j, i} | v_i) p(v_i)}{p( p_{j, i})} \propto p(p_{j,i} | v_i) p(v_i).
\end{align}
From the properties of Gaussian distributions, the posterior probability given a measurement is also distributed according to a Gaussian distribution~\cite{bishop2006} and given by
\begin{align}\label{eq:posterior_probability}
    \mathcal{N} \parenth{\frac{w_{j, i}^2 r_i + w_i^2 r_{j, i}}{w_i^2 + w_{j, i}^2} , \frac{w_i^2  w_{j, i}^2}{w_i^2 +  w_{j, i}^2}} .
\end{align}
From~\cref{eq:posterior_probability}, the a posterior mean conditioned on the measurement is the average of the prior knowledge and the measurement weighted by the reciprocal of the variance. 
As such, it will be closer to the value with a smaller variance. 
For example, measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the radial position of the vertex.

@@

The results in this section utilize a kinematics only model of the spacecraft instead of the full dynamical simulation. 
We ignore the dynamics of the asteroid and spacecraft and instead focus solely on the shape reconstruction, and the spacecraft is assumed to be able to arbitrarily move around the asteroid and collect measurements.
The spacecraft remains at a fixed orbital radius defined as twice the maximum semi-major axis of the asteroid.
The simulations begin with an triaxial ellipsoid mesh that is sized to match the semi-major axes of each asteroid.
With this estimate, measurements are made of the surface and used to reconstruct the true shape following the process in~\cref{sec:radius_update}.
LIDAR measurements are generated until the total uncertainty of the model
\begin{align*}
    \sum_i w_i,
\end{align*}
is sufficiently small.
This uncertainty metric is the summation of the uncertainty of each vertex of the shape estimate.
As a result, a small total uncertainty is used to indicate that additional measurements would not substantially modify the shape.
In addition, we compute the volume of the estimated shape and compare it against the volume of the truth shape model~\cite{neese2004}.

@@

\paragraph{Asteroid \num{1620} Geographos Reconstruction} 
\num{1620} Geographos is a highly elongated stony asteroid of the Apollo group.
Discovered in \num{1951}, Geographos is a potentially hazardous asteroid which passes sufficiently close to the Earth.
\Cref{fig:geographos_reconstruction} shows the shape reconstruction for asteroid Geographos at several distinct points during the process.
Comparing~\cref{fig:geographos_partial_100,fig:geographos_truth} shows that the final shape closely matches the true radar model.
In~\cref{fig:geographos_metrics} we display the vertex uncertainty and mesh volume as a function of time.
The plots show that the reconstruction achieves an accurate shape estimate with a total volume which closely matches the true volume.

@@

\paragraph{Asteroid \num{6489} Golevka Reconstruction} 
Next, \num{6489} Golevka is a small angular shaped asteroid of the Apollo group.
Discovered in \num{1995}, Golevka is another potentially hazardous asteroid which passes close to the Earth.
\Cref{fig:golevka_reconstruction} shows the shape reconstruction for asteroid Golevka at several distinct points during the process.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Initial Shape Estimate\label{fig:golevka_partial_0}}{\includegraphics[trim={20cm 5cm 20cm 5cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_0.jpg}}%
    \subcaptionbox{\SI{25}{\percent} of measurements added\label{fig:golevka_partial_25}}{\includegraphics[trim={20cm 10cm 20cm 10cm},clip,keepaspectratio,width=0.5\textwidth,height=0.25\textheight]{mesh_update_golevka_partial_1321.jpg}}\\%

@@

We define a cost associated with each vertex \( \vc{v}_i \) of the shape estimate as
\begin{align}\label{eq:explore_cost}
    J_i (x, R, R_A) = \alpha_w J_{w_i} + \alpha_d J_{d_i}(x_r) + \alpha_c J_{c_i}(x_r)
\end{align}
where the weighting factors \( \alpha_w, \alpha_d, \alpha_c \in \R \) are chosen such that \( \alpha_w + \alpha_d + \alpha_c = 1 \).
The cost function is defined as a function of the current inertial position, \( x \in \R^3 \), and the attitude, \( R \in \R^{3\times3}\) of the spacecraft.
Furthermore, the knowledge of the small body rotation is required in order to determine the position of the spacecraft in the small body fixed frame, \( x_r = R_A^T x\).

@@

Finally, a control component is included in the cost function which penalizes vertices that are difficult to reach.
Consider, the current position of the spacecraft in the small body fixed frame as \( \rpos\) and a desired vertex \( \vc{v}_i \) of the shape estimate.
We can define a normal vector to the plane spanned by \( \rpos, \vc{v}_i \) as
\begin{align}\label{eq:normal_to_plane}
    \vc{n}_i = \frac{\rpos \times \vc{v}_i}{\norm{\rpos} \norm{\vc{v}_i}}.
\end{align}
Then a desired trajectory \( x_d(\theta) \) as
\begin{align}\label{eq:spherical_waypoint}
    x_d(\theta) = r_d \exp{\parenth{\theta \hat{\vc{n}_i}} } \frac{\rpos}{\norm{\rpos}},
\end{align}
where \( \theta : \bracket{0, \frac{\rpos \cdot \vc{v}_i}{\norm{\rpos}\norm{\vc{v}_i}}} \to \R\) parameterizes the desired trajectory.
\Cref{eq:spherical_waypoint} simply describes a portion of a great circle trajectory between the current state, \( \rpos \), and the desired vertex \( \vc{v}_i \)~\cite{chen2016}, with a desired radius $r_d$.
The radius of the spacecraft, \( r_d \in \R \), can be chosen based on sensor characteristics of safety concerns.
For example, \( r_d \) can be chosen as the distance of the Biroullin sphere with an additional safety margin to mitigate any surface collision~\cite{scheeres2012a}.

@@

The selection of a landing site will typically require a vast quantity of data and weigh a multitude of possible metrics, such as scientific value, hardware constraints, timing and communication limits, or safety considerations. 
In our analysis we consider the surface slope, the distance to the surface, and a fictitious science metric in order to determine the best landing site based on the complete shape estimate.
This approach allows for a spacecraft to autonomously select and to land on small body.

The surface slope is computed according to the method developed in Reference~\cite{scheeres1996}.
Due to the small size, and therefore low gravitational attraction, the force at each point on the surface is a combination of the gravitational attraction and the centripetal acceleration.
At the center of each face, \( f_i = [ f_x,\,  f_y,\,  f_z ] \), we compute a modified surface acceleration as
\begin{align}\label{eq:surface_force}
    U_m = \omega^2 \begin{bmatrix} f_x \\ f_y \\ 0 \end{bmatrix} + \begin{bmatrix} U_x \\ U_y \\ U_z \end{bmatrix},
\end{align}
where \( \omega \in \R^1 \) is the angular velocity of the asteroid and \( U_i \) is computed from~\cref{eq:attraction}.
Then the surface slope can be computed from
\begin{align}\label{eq:surface_slope}
    \cos \parenth{ \pi - \phi } = \frac{\vc{n}_f \cdot U_m}{\norm{U_m}},
\end{align}
where \( \phi \in \R \) is the surface slope defines the angle between the surface normal \( \vc{n}_f \in \R^3 \) and the force vector at the surface.
If \( \phi = \SI{0}{\degree} \) then the force vector and the surface normal are anti-parallel, while \( \phi > \SI{90}{\degree} \) means that a particle on the surface would be thrown off the body as the centripetal force is larger than the gravitational attraction.
